
```{r normal approximation to poisson}

par(mfrow=c(1,3))
plot(0:10, dpois(0:10, lambda = 2), type = "l", lwd=2, col ='steelblue', frame.plot = F)
#polygon(c(0:10), c(dpois(0:10, lambda=10)), col="skyblue", border = "steelblue")
plot(0:20, dpois(0:20, lambda = 10), type = "l", col="orange", lwd=2, frame.plot = F)
#polygon(c(0:20), c(dpois(0:20, lambda=10)), col="darkgreen", border = "orange")
plot(0:200, dpois(0:200, lambda = 100), type = "l", col="tomato", lwd=2, frame.plot = F)
#polygon(c(0:200), c(dpois(0:200, lambda=100)), col="tomato", border = "orange")

```
Binary outcomes-
Alive/Dead
Win/losses
Success/Failures

COnsider modelling coin flips where success depends on a bunch of covariates.

Binomial Random Variable-If we have a collection fo zeros and ones where success probability is contant and they're independent, then, the total number of success or failures is called binomial random variable.

Binomial Random Variable are handled by binary logistic regression in the special case where covariates are just constant.

```{r }
#Loading ravens data already present in the working directory: SPecify download source
load("./ravensData.rda")
head(ravensData)
#Examining if Raven's score has an impact on their Win/loss


lmRavens <- lm(ravensData$ravenWinNum ~ ravensData$ravenScore)
summary(lmRavens)

```

```{r}
head(shuttle)
```










```{r}
library(MASS)
?shuttle
data("shuttle")
head(shuttle)

my_logistic<-glm(use~wind, data = shuttle, family = "binomial")
exp(coef(my_logistic))

my_logistic<-glm(use~wind+magn, data = shuttle, family = "binomial")
exp(coef(my_logistic))


```


```{r}
library(MASS)
data(shuttle)
## Make our own variables just for illustration
shuttle$auto <- 1 * (shuttle$use == "auto")
shuttle$headwind <- 1 * (shuttle$wind == "head")
fit <- glm(auto ~ headwind, data = shuttle, family = binomial)
exp(coef(fit))

## (Intercept)    headwind 
##      1.3273      0.9687

## Another way without redifing variables
fit <- glm(relevel(use, "noauto") ~ relevel(wind, "tail"), data = shuttle, family = binomial)
exp(coef(fit))

##               (Intercept) relevel(wind, "tail")head 
##                    1.3273                    0.9687

my_logistic<-glm(auto~headwind , data = shuttle, family = "binomial")
exp(coef(my_logistic))
```

```{r}
my_logistic_inv<-glm((1-auto)~headwind, data = shuttle, family = "binomial")
exp(coef(my_logistic_inv))
```


Insectsprays
```{r Insectsprays}
ins_spray<-glm(count~spray, data = InsectSprays, family = "poisson")
coef(ins_spray)

getwd()
```
5-Consider a Poisson glm with an offset, t. So, for example, a model of the form glm(count ~ x + offset(t), family = poisson) where x is a factor variable comparing a treatment (1) to a control (0) and t is the natural log of a monitoring time. What is impact of the coefficient for x if we fit the model glm(count ~ x + offset(t2), family = poisson) where 2 <- log(10) + t? In other words, what happens to the coefficients if we change the units of the offset variable. (Note, adding log(10) on the log scale is multiplying by 10 on the original scale.)
Ans
5-The coefficient estimate is unchanged. Note, the coefficients are unchanged, except the intercept, which is shifted by log(10). Recall that, except the intercept, all of the coefficients are interpretted as log relative rates when holding the other variables or offset constant. Thus, a unit change in the offset would cancel out. This is not true of the intercept, which is interperted as the log rate (not relative rate) with all of the covariates set to 0.
```{r}
x <- -5:5
y <- c(5.12, 3.93, 2.67, 1.87, 0.52, 0.08, 0.93, 2.05, 2.54, 3.87, 4.97)
z <- (x > 0) * x
fit <- lm(y ~ x + z)
sum(coef(fit)[2:3])
```
